\thornado-hydro: Generalizing discontinuous Galerkin methods for a nuclear equation of state for supernova hydrodynamics

### 2019-05-06 paper/ms.tex
Found an error.

\subsection{EOS Table Sensitivity}
In order to probe the sensitivity of the method to the EOS table, we repeated
the tests conducted in Section~\ref{sec:optimal} using three different EOS tables:
the high resolution SFHo table from Section~\ref{sec:eosRes}, the SFHx table
(\textbf{citation}), and the DD2 table (\textbf{citation}).
As before, tests are computed using 100 elements until
$t = 0.025$ms with characteristic limiting and the optimal limiting parameters determined in
Section~\ref{sec:param}. We find nearly no sensitivity to the EOS table used in
the low density regime, with the exception of very small variations in density
to the left of the contact discontinuity. Future work includes testing the
sensitivity to the EOS table in higher density regimes.
\begin{figure}[h!]
  \centering
  \includegraphics[width=36pc]{./figures/eos_all.png}
  \caption{\label{fig:SodSedovEOS} Comparison of numerical solutions to
  Sod's problem using 100 elements with characteristic limiting and three
  different EOS tables for density (upper left), pressure (upper right),
  velocity (lower left), and electron fraction (lower right).
  }
\end{figure}
%\FloatBarrier

>>>>

\subsection{EOS Table Sensitivity}
In order to probe the sensitivity of the method to the EOS table, we repeated
the tests conducted in Section~\ref{sec:optimal} using three different EOS tables:
the high resolution SFHo table from Section~\ref{sec:eosRes}, the SFHx table, and the DD2 table.
As before, tests are computed using 100 elements until
$t = 0.025$ms with characteristic limiting and the optimal limiting parameters determined in
Section~\ref{sec:param}. We find nearly no sensitivity to the EOS table used in
the low density regime, with the exception of very small variations in density
to the left of the contact discontinuity. Future work includes testing the
sensitivity to the EOS table in higher density regimes.
\begin{figure}[h!]
  \centering
  \includegraphics[width=36pc]{./figures/eos_all.png}
  \caption{\label{fig:SodSedovEOS} Comparison of numerical solutions to
  Sod's problem using 100 elements with characteristic limiting and three
  different EOS tables for density (upper left), pressure (upper right),
  velocity (lower left), and electron fraction (lower right).
  }
\end{figure}
%\FloatBarrier
